 

### 2023-03-02 appendix_2.1.Rmd
Revisions to make dplyr::select command run without errors, revisions to Paper 3

data %>% filter(sex == "both" & subgroup == "total") %>% 
    group_by(disease, year) %>%
    # mutate(count = sum(count)) %>% 
    # filter(count != 0 & count != 14 & count != 7 & count != 21 & count != 28 & count != 35 & count != 42  & count != 49  & count != 56  & count != 63  & count != 70) %>% 
    # ungroup() %>%
    # select(clinic_name, disease, year, ) %>%
    # unique() %>%
    # mutate(n = 1) %>% 
    # group_by(year, disease) %>%  
    mutate(sum = sum(count)) %>%  
    select(sum, year, disease) %>% 
    ungroup() %>%
    unique() %>% 
  left_join(mh_english_disease, by = "disease") %>%
  mutate(disease = paste0(disease_english, " (", 
                          StrTrunc(disease, maxlen = 25, ellipsis = "...", wbound = TRUE),")")) %>%
      select(year, disease, sum) %>%
    rename(Year = year, Total = sum) %>%
  mutate(disease = gsub(" and ", " & ", disease),
         disease = case_when(

@@

n_chu <- chu_data %>% select(disease) %>% unique() %>% nrow

@@

  ## Add English translations for diseases, drop French disease names
  left_join(., mh_english_disease, by = "disease") %>%
  select(!c(disease)) %>%
  rename(disease = disease_english) %>%
  relocate(disease, .after = clinic_name) %>%

@@

## Create a unique facility ID based on the clinic name and location
data_mh_temp <- data_mh %>%
  select(clinic_name, region_name, district_name, commune_name) %>%
  unique() %>%
  arrange(clinic_name, region_name, district_name, commune_name) %>%
  mutate(facility_ID = seq.int(nrow(.)))

@@

data_mh_temp <- data_mh %>%
   select(!c(disease, count)) %>%
   unique() %>%
   pivot_longer('Any mental or neurological disorders', names_to = "disease", values_to = "count")

data_mh <- data_mh %>%
  select(!c('Any mental or neurological disorders')) %>%
  rbind(., data_mh_temp)

@@

data_mh %>% filter(sex == "both") %>% select(clinic_name, district_name, region_name, commune_name) %>% unique() %>% nrow()

@@

<!-- data_facility_reporting <- data_mh %>%  -->
<!--   filter(disease == "Any mental or neurological disorders") %>% -->
<!--   filter(sex == "both") %>% -->
<!--   filter(subgroup == "total") %>% -->
<!--   filter(cleaning_status == "count_raw") %>% -->
<!--   mutate(reporting = ifelse(count == 0, NA, "Yes")) %>% -->
<!--   select(date, region_name, district_name, commune_name, clinic_name_clean, clinic_type, reporting) %>% -->
<!--   unique() -->

<!-- duplicate_name_facilities <- data_facility_reporting %>% -->
<!--   select(region_name, district_name, commune_name, clinic_name_clean, clinic_type) %>% -->
<!--   unique() %>% -->
<!--   mutate(full_string = paste0(region_name, district_name, commune_name, clinic_name_clean)) -->

@@

<!-- data_facility_reporting %>% -->
<!--   filter(!is.na(reporting)) %>% -->
<!--   mutate(full_string = paste0(region_name, district_name, commune_name, clinic_name_clean)) %>% -->
<!--   filter(full_string %in% duplicates) %>% -->
<!--   select(!full_string) %>% -->
<!--   arrange(clinic_name_clean) %>% -->
<!--   group_by(region_name, district_name, commune_name, clinic_name_clean) %>% -->
<!--   mutate(n=1) %>% -->
<!--   mutate(sum1 = sum(n, na.rm = TRUE)) %>% -->
<!--   ungroup() %>% -->
<!--   group_by(region_name, district_name, commune_name, clinic_type) %>% -->
<!--   mutate(sum2 = sum(n, na.rm = TRUE)) %>% -->
<!--   ungroup() %>% -->
<!--   filter(sum2 != sum1) %>% -->
<!--   unique() %>% -->
<!--   mutate(date = as.Date(date)) %>% -->
<!--   ggplot(aes(x = date, y = clinic_type, fill = reporting)) + -->
<!--   geom_tile() + -->
<!--   facet_wrap(~clinic_name_clean, scales = "free_y") + -->
<!--   theme(text = element_text(family = "Source Sans Pro")) + -->
<!--   theme(legend.position = "none")  + -->
<!--   scale_x_date(date_labels = "%Y") + -->
<!--   labs(x = "Date", y = "") + -->
<!--   theme_classic() -->

@@

<!-- duplicate_name_facilities %>% -->
<!--   filter(full_string %in% duplicates) %>% -->
<!--   select(!full_string) %>% -->
<!--   arrange(clinic_name_clean) %>% -->
<!--   group_by(region_name, district_name, commune_name, clinic_name_clean) %>% -->
<!--   summarise(clinic_type = paste(clinic_type, collapse = " | ")) %>% -->
<!--   ungroup() %>% -->
<!--   unique() %>% -->
<!--   select(clinic_name_clean, clinic_type) %>% -->
<!--   rename("Facility name" = clinic_name_clean, -->
<!--          "Types" = clinic_type) %>% -->
<!--   gt() %>%  -->
<!--   tab_header( -->
<!--     title = md("**Examples of duplicate facility names in different regions**")) %>% -->
<!--   tab_options(table.font.names = "Source Sans Pro") %>% -->
<!--   tab_style( -->
<!--     locations = cells_column_labels(), -->
<!--     style     = list( -->
<!--       cell_text(weight = "bold")) -->
<!--   ) -->

@@

## variable_descrip <- data_raw %>% select(description) %>% unique()
## variable_name <- data_raw %>% select(variable) %>% unique()
## variable_tabname <- data_raw %>% select(table_name) %>% unique()
## variable_medco <- data_raw %>% select(medical_code) %>% unique()

@@

##   select(code, description) %>% 

@@

##   select(date, count) %>%

@@

## facilities_clinic_codes <- data_raw %>% select(clinic_code) %>% unique()
## facilities_district_codes <- data_raw %>% select(district_code) %>% unique()

@@

##   select(district_code, clinic_code, name) %>%

@@

##   select(district_code, district_type, name) %>%

@@

##   select(Nom.complet.FS.1, latitude, longitude) %>% 

@@

##   select(district_name, ADM2_PCODE)

@@

##   select(district_code, district_name, ADM2_PCODE) %>%

@@

## facilities_map_clean <- facilities_map %>% select(clinic_code:clinic_name) %>%

@@

##   select(!c(district_name)) %>%

@@

##   select(ADM2_PCODE, district_name, district_code, geometry) %>%

>>>>

data %>% filter(sex == "both" & subgroup == "total") %>% 
    group_by(disease, year) %>%
    # mutate(count = sum(count)) %>% 
    # filter(count != 0 & count != 14 & count != 7 & count != 21 & count != 28 & count != 35 & count != 42  & count != 49  & count != 56  & count != 63  & count != 70) %>% 
    # ungroup() %>%
    # dplyr::select(clinic_name, disease, year, ) %>%
    # unique() %>%
    # mutate(n = 1) %>% 
    # group_by(year, disease) %>%  
    mutate(sum = sum(count)) %>%  
    dplyr::select(sum, year, disease) %>% 
    ungroup() %>%
    unique() %>% 
  left_join(mh_english_disease, by = "disease") %>%
  mutate(disease = paste0(disease_english, " (", 
                          StrTrunc(disease, maxlen = 25, ellipsis = "...", wbound = TRUE),")")) %>%
      dplyr::select(year, disease, sum) %>%
    rename(Year = year, Total = sum) %>%
  mutate(disease = gsub(" and ", " & ", disease),
         disease = case_when(

@@

n_chu <- chu_data %>% dplyr::select(disease) %>% unique() %>% nrow

@@

  ## Add English translations for diseases, drop French disease names
  left_join(., mh_english_disease, by = "disease") %>%
  dplyr::select(!c(disease)) %>%
  rename(disease = disease_english) %>%
  relocate(disease, .after = clinic_name) %>%

@@

## Create a unique facility ID based on the clinic name and location
data_mh_temp <- data_mh %>%
  dplyr::select(clinic_name, region_name, district_name, commune_name) %>%
  unique() %>%
  arrange(clinic_name, region_name, district_name, commune_name) %>%
  mutate(facility_ID = seq.int(nrow(.)))

@@

data_mh_temp <- data_mh %>%
   dplyr::select(!c(disease, count)) %>%
   unique() %>%
   pivot_longer('Any mental or neurological disorders', names_to = "disease", values_to = "count")

data_mh <- data_mh %>%
  dplyr::select(!c('Any mental or neurological disorders')) %>%
  rbind(., data_mh_temp)

@@

data_mh %>% filter(sex == "both") %>% dplyr::select(clinic_name, district_name, region_name, commune_name) %>% unique() %>% nrow()

@@

<!-- data_facility_reporting <- data_mh %>%  -->
<!--   filter(disease == "Any mental or neurological disorders") %>% -->
<!--   filter(sex == "both") %>% -->
<!--   filter(subgroup == "total") %>% -->
<!--   filter(cleaning_status == "count_raw") %>% -->
<!--   mutate(reporting = ifelse(count == 0, NA, "Yes")) %>% -->
<!--   dplyr::select(date, region_name, district_name, commune_name, clinic_name_clean, clinic_type, reporting) %>% -->
<!--   unique() -->

<!-- duplicate_name_facilities <- data_facility_reporting %>% -->
<!--   dplyr::select(region_name, district_name, commune_name, clinic_name_clean, clinic_type) %>% -->
<!--   unique() %>% -->
<!--   mutate(full_string = paste0(region_name, district_name, commune_name, clinic_name_clean)) -->

@@

<!-- data_facility_reporting %>% -->
<!--   filter(!is.na(reporting)) %>% -->
<!--   mutate(full_string = paste0(region_name, district_name, commune_name, clinic_name_clean)) %>% -->
<!--   filter(full_string %in% duplicates) %>% -->
<!--   dplyr::select(!full_string) %>% -->
<!--   arrange(clinic_name_clean) %>% -->
<!--   group_by(region_name, district_name, commune_name, clinic_name_clean) %>% -->
<!--   mutate(n=1) %>% -->
<!--   mutate(sum1 = sum(n, na.rm = TRUE)) %>% -->
<!--   ungroup() %>% -->
<!--   group_by(region_name, district_name, commune_name, clinic_type) %>% -->
<!--   mutate(sum2 = sum(n, na.rm = TRUE)) %>% -->
<!--   ungroup() %>% -->
<!--   filter(sum2 != sum1) %>% -->
<!--   unique() %>% -->
<!--   mutate(date = as.Date(date)) %>% -->
<!--   ggplot(aes(x = date, y = clinic_type, fill = reporting)) + -->
<!--   geom_tile() + -->
<!--   facet_wrap(~clinic_name_clean, scales = "free_y") + -->
<!--   theme(text = element_text(family = "Source Sans Pro")) + -->
<!--   theme(legend.position = "none")  + -->
<!--   scale_x_date(date_labels = "%Y") + -->
<!--   labs(x = "Date", y = "") + -->
<!--   theme_classic() -->

@@

<!-- duplicate_name_facilities %>% -->
<!--   filter(full_string %in% duplicates) %>% -->
<!--   dplyr::select(!full_string) %>% -->
<!--   arrange(clinic_name_clean) %>% -->
<!--   group_by(region_name, district_name, commune_name, clinic_name_clean) %>% -->
<!--   summarise(clinic_type = paste(clinic_type, collapse = " | ")) %>% -->
<!--   ungroup() %>% -->
<!--   unique() %>% -->
<!--   dplyr::select(clinic_name_clean, clinic_type) %>% -->
<!--   rename("Facility name" = clinic_name_clean, -->
<!--          "Types" = clinic_type) %>% -->
<!--   gt() %>%  -->
<!--   tab_header( -->
<!--     title = md("**Examples of duplicate facility names in different regions**")) %>% -->
<!--   tab_options(table.font.names = "Source Sans Pro") %>% -->
<!--   tab_style( -->
<!--     locations = cells_column_labels(), -->
<!--     style     = list( -->
<!--       cell_text(weight = "bold")) -->
<!--   ) -->

@@

## variable_descrip <- data_raw %>% dplyr::select(description) %>% unique()
## variable_name <- data_raw %>% dplyr::select(variable) %>% unique()
## variable_tabname <- data_raw %>% dplyr::select(table_name) %>% unique()
## variable_medco <- data_raw %>% dplyr::select(medical_code) %>% unique()

@@

##   dplyr::select(code, description) %>% 

@@

##   dplyr::select(date, count) %>%

@@

## facilities_clinic_codes <- data_raw %>% dplyr::select(clinic_code) %>% unique()
## facilities_district_codes <- data_raw %>% dplyr::select(district_code) %>% unique()

@@

##   dplyr::select(district_code, clinic_code, name) %>%

@@

##   dplyr::select(district_code, district_type, name) %>%

@@

##   dplyr::select(Nom.complet.FS.1, latitude, longitude) %>% 

@@

##   dplyr::select(district_name, ADM2_PCODE)

@@

##   dplyr::select(district_code, district_name, ADM2_PCODE) %>%

@@

## facilities_map_clean <- facilities_map %>% dplyr::select(clinic_code:clinic_name) %>%

@@

##   dplyr::select(!c(district_name)) %>%

@@

##   dplyr::select(ADM2_PCODE, district_name, district_code, geometry) %>%
